%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {INESC TEC} % Organization
    {Braga, Portugal} % Location
    {Sep. 2014 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborated on the development and deployment of \href{https://stayaway.inesctec.pt}{Stayaway Covid}.}
        \begin{itemize}
          \item Stayaway Covid is the official contact tracing Portuguese application in response to the Covid Pandemic.
          \item Analyzed the security of the underlying cryptographic protocol (DP-3T).
          \item Helped write the content and define the interface of the project's webpage \href{http://stayaway.inesctec.pt}{http://stayaway.inesctec.pt}.
        \end{itemize}
        \item{Collaborated in the European \href{https://www.safecloud-project.eu}{SafeCloud} project.}
        \begin{itemize}
          \item Developed database engines and file systems.
          \item Helped write project deliverables.
          \item Automated the deployment of several project components using containers.
          \item Managed the successful integration of the project databases with industry partners.
          \item More information on the project in \href{https://www.safecloud-project.eu}{https://www.safecloud-project.eu}.
        \end{itemize}
        \item{Full-stack developer in \href{https://falarsobrecancro.org}{FalarSobreCancro.org}, a social network to help the Portuguese oncology community.}
        \item{Developer in the national \href{https://haslab.uminho.pt/content/haslab-concludes-project-pt-inovacaoaltice-labs}{OSSAS} research project.}
        \begin{itemize}
            \item More information on the project in \href{https://haslab.uminho.pt/content/haslab-concludes-project-pt-inovacaoaltice-labs}{https://haslab.uminho.pt/content/haslab-concludes-project-pt-inovacaoaltice-labs}.
        \end{itemize}
        \item{External reviewer of computer science conferences (SRDS 2019, DSN 2019, Crypto 2019).}
        \item{Supervised two master students dissertations. Both defended successfully.}
        \item{Helped write European project proposals.}
        \item {Implemented front-end components on several WordPress websites (\href{https://aida.inesctec.pt}{Aida}, \href{https://bighpc.wavecom.pt}{BigHPC}, \href{http://formalmethods2019.inesctec.pt}{FM2019}, \href{https://eurosys2018.org}{EuroSys2018}).}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
